### 2014-03-11 etc/abstract.tex
Updated paper to use cached knitr, and updated abstract to say what we achieved.

% 1.Statetheproblem
Mutation analysis is a metric for measuring the quality of test suites. However, its exorbitant computational requirements makes it hard to use in practice. Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.

%2.Saywhyit’saninterestingproblem
However, how best to choose among multiple selection criterias is an open problem, especially for real-world programs and test-suites.

%3.Saywhatyoursolutionachieves
Our research compare a number of selection criteria along different dimensions including prediction of original mutation score, mutant reduction ratio, and time for completion.

%4.Saywhatfollowsfromyoursolution

>>>>

% 1.Statetheproblem
Mutation analysis is a metric for measuring the quality of test suites. However, it is computationally intensive compared to other measures which it hard to use in practice. Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem. There exist multiple ways to reduce the set of mutations to run. Operator selection is an area that has been heavily researched. Recently, researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.

%2.Saywhyit’saninterestingproblem
However, the statistical inference that can be drawn from these research has been limited due to the small number of subject programs. Further, which sampling technique is best is still an open problem that needs to be tackled on a much larger range of test subjects.

%3.Saywhatyoursolutionachieves
Our research compares a number of sampling criteria, and operator selection criteria based on their ability to approximate the full mutation score, and also the consistency of mutation reduction ratios achieved. Our results provide a ranking that can be used to choose an appropriate mutation reduction technique according to the mutation reduction ratio desired, and how much reduction in accuracy is acceptable.
%4.Saywhatfollowsfromyoursolution

We find that all sampling criterias perform better than operator selection methods when considering their ability to predict the full mutation score, and also the consistency of mutation reduction ratios achieved.
We find that simplest sampling criteria --- sampling based on projects works best on all the factors examined, We provide an explanation for this result, and why this is important for future research.
